Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-02-14 paper-ieee-trans.tex
Update paper-ieee-trans.tex

\bibitem{disvis} G.C.P. Van Zundert, A.M.J.J. Bonvin,
DisVis: quantifying and visualizing the accessible interaction space of distance
restrained biomolecular complexes, Bioinformatics 31 (2015) 3222???3224

\bibitem{powerfit} G.C.P. Van Zundert, A.M.J.J. Bonvin,
Fast and sensitive rigid-body fitting into cryo-EM density maps with PowerFit,
AIMS Biophys. 2 (2015) 73???87.

>>>>

\bibitem{disvis} G.C.P. Van Zundert, A.M.J.J. Bonvin,
DisVis: quantifying and visualizing the accessible interaction space of distance
restrained biomolecular complexes, Bioinformatics 31 (2015) 3222--3224

\bibitem{powerfit} G.C.P. Van Zundert, A.M.J.J. Bonvin,
Fast and sensitive rigid-body fitting into cryo-EM density maps with PowerFit,
AIMS Biophys. 2 (2015) 73--87.
